%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-.70in}
\addtolength{\evensidemargin}{-.70in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{-0.0625in}

% Sections formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\footnotesize{#1}
    {\vspace{-2pt}}
  }

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \small#2 \\
      \textit{\footnotesize#3} & \textit{\footnotesize #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\footnotesize#1} & \textit{\footnotesize #2} \\
    \end{tabular*}\vspace{-12pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \footnotesize#1 & \footnotesize#2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\hspace{0.5em}\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Large \scshape Michael Huang} \\ \vspace{3pt}
    \small 
    \href{mailto:michael.yuki.huang@gmail.com}{{michael.yuki.huang@gmail.com}} $\cdot$
    \href{https://gitmichaelhuang.github.io}{{gitmichaelhuang.github.io}} $\cdot$  
    \href{https://linkedin.com/in/michaelhuang6}{{linkedin.com/in/michaelhuang6}} $\cdot$
    \href{https://github.com/gitmichaelhuang}{{github.com/gitmichaelhuang}}
\end{center} \vspace{-16pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubSubheading
      {\small \normalfont \textbf{University of Illinois Urbana Champaign --} {Bachelor of Science, Statistics}} {\small \normalfont Aug 2020 -- May 2024} \\ \vspace{8pt}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


\section{Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
      {DuPage County, Election Division}{Oct 2024 -- Present}
      {Warehouse Laborer}{Aurora, IL}
      \resumeItemListStart
        \resumeItem{Evaluate, maintain, and assist in operations, machinery, and processes related to the 2024 General Election and 2025 local elections.}
    \resumeItemListEnd

    \resumeSubheading
    {Blue Modern Advisory}{Jun 2023 -- Aug 2023}
    {Software Engineer Intern}{Remote}
    \resumeItemListStart
      \resumeItem{Designed and implemented a robust web scraping system using Beautiful Soup and Selenium that extracts structured data from diverse job posting formats.}
      \resumeItem{Assisted in building a real-time monitoring dashboard for web scraping operations, allowing instant identification and resolution of extraction failures.}
      \resumeItem{Designed data cleansing algorithms that normalized and structured raw scraped job data, improving data quality scores.}
    \resumeItemListEnd

    \resumeSubheading
      {Favors}{Jun 2022 -- Aug 2022}
      {Software Engineer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Developed and implemented React Native components for the Favors Android app, improving user engagement through an intuitive favor request interface}
        \resumeItem{Collaborated in an Agile development team to build RESTful API endpoints using Node.js and Express, handling geolocation-based favor discovery and user matching}
        \resumeItem{Assisted in setting up CI/CD pipelines using GitHub Actions, streamlining the development and deployment workflow}
    \resumeItemListEnd

    \resumeSubheading
      {Advanced Computer Communications Technologies}{Jun 2021 -- Aug 2021}
      {Software Engineer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Created an API that delivers spend summary statistics, pulling data from Amazon S3 and transforming it into accessible formats.}
        \resumeItem{Built a secure login system with proper data handling protocols, using AWS DynamoDB for user data storage and created a custom API to expose relevant statistics.}
        \resumeItem{Implemented AWS Lambda functions to automatically aggregate and analyze customer records for spend pattern identification.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{TaskFlow} \emph{}}{}
          \resumeItemListStart
            \resumeItem{A full-stack project management app built with React, Node.js, MongoDB, and Tailwind CSS. This application allows users to create projects, manage tasks, and track progress with a clean, modern interface. It includes features like user authentication, task boards, real-time statistics, and visualization of task completion data.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{MealMinder} \emph{}}{}
          \resumeItemListStart
            \resumeItem{A comprehensive full-stack application for meal planning and recipe management. Users can browse recipes, create meal plans for the week, and generate shopping lists automatically. Built with React, Node.js, MongoDB, and Tailwind CSS, it features recipe search and filtering, meal calendar visualization, and automatic shopping list generation based on planned meals.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{GalaxyDefenders} \emph{}}{}
          \resumeItemListStart
            \resumeItem{A modern browser-based space shooter game with clean visuals and engaging gameplay. Players defend Earth from alien invaders, collecting power-ups and fighting bosses as they progress through increasingly difficult levels. The game is built with vanilla JavaScript and features responsive controls that work on both desktop and mobile devices.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Maze Solver} \emph{}}{}
          \resumeItemListStart
            \resumeItem{Created an efficient maze generation system capable of producing complex mazes with varying difficulty levels using randomized Prim's algorithm and recursive backtracking}
            \resumeItem{Integrated real-time performance metrics and algorithm comparison visualizations that highlight differences in node exploration patterns between solving methods}
        \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{Computer Vision Mood Analyzer} \emph{}}{}
          \resumeItemListStart
            \resumeItem{Developed a React-based web application that captures and analyzes facial data using webcam integration to identify user mood.}
            \resumeItem{Implemented responsive camera controls and UI components using React Hooks for efficient state management and real-time webcam processing.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
   \footnotesize{\item{
    \textbf{Languages}{: JavaScript, Python, HTML/CSS, SQL, Java, TypeScript, C++} \\
    \textbf{Technologies}{: React, React Native, Node.js, Express, MongoDB, AWS (S3, DynamoDB, Lambda), GitHub Actions, Tailwind CSS, Beautiful Soup, Selenium, CI/CD, RESTful APIs, Git, Agile methodologies} \\
    \textbf{Interests}{: Basketball, Running, Health, Geography, History}
   }}
\end{itemize}

\end{document}